Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-24 analysis/paper/paper.Rmd
updated objectives to reflect moving 'Adult Impacts'

We hypothesize that increased densities of piscivorous predators in the Deadwater Slough may explain the reduced survival (or apparent survival) observed for juvenile Chinook Salmon [@Ackerman2018] and Sockeye Salmon [@Axel2015]. In this study, we estimated the abundance of a piscivorous fish predator population in the Deadwater Slough and their potential impacts to juvenile salmon emigrants, focusing on DSR and NRR Chinook Salmon. Our objectives for the study were four-fold:

1. Estimate the abundance (or relative abundance) of potential predators in the Deadwater Slough during the peaks of fall (DSR) and spring (NRR) juvenile emigrations.
2. Document predation on juvenile Chinook Salmon during the emigration periods using gastric lavage.
3. Use a bioenergetics approach to estimate the total consumption of juvenile DSR and NRR Chinook salmon during defined emigration periods.
4. Quantify the potential impacts of estimated predation on juvenile to Chinook Salmon adult returns.

We follow with a discussion of the various assumptions that went into the mark-recapture and bioenergetics models and assessment of impacts to adult returns and how violations of some assumptions may affect overall results and inferences from the study.

@@

>>>>

We hypothesize that increased densities of piscivorous predators in the Deadwater Slough may explain the reduced survival (or apparent survival) observed for juvenile Chinook Salmon [@Ackerman2018] and Sockeye Salmon [@Axel2015]. In this study, we estimated the abundance of a piscivorous fish predator population in the Deadwater Slough and their potential impacts to juvenile salmon emigrants, focusing on DSR and NRR Chinook Salmon. Our objectives for the study were three-fold:

1. Estimate the abundance (or relative abundance) of potential predators in the Deadwater Slough during the peaks of fall (DSR) and spring (NRR) juvenile emigrations.
2. Document predation on juvenile Chinook Salmon during the emigration periods using gastric lavage.
3. Use a bioenergetics approach to estimate the total consumption of juvenile DSR and NRR Chinook salmon during defined emigration periods.

We follow with a discussion of the various assumptions that went into the mark-recapture and bioenergetics models and how violations of some assumptions may affect overall results and inferences from the study. We also consider how consumption of juvenile Chinook Salmon by predators at Deadwater Slough might impact adult returns, hindering recovery of populations in the Upper Salmon River MPG.

@@

<!-- START HERE -->
